---
title: "Introduction to R"
name: "your name"
date: 

output:
  html_document:
    css: ../lab.css
    highlight: pygments
    theme: cerulean
    toc: true
    toc_float: true
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(eval = TRUE)
library(tidyverse)
```

## R Packages

Loading needed Packages
```{r install-packages, message = FALSE, eval=FALSE}
install.packages("tidyverse")
install.packages("devtools")
library(devtools)
install_github("OpenIntroStat/openintro-r-package")
```

`library` is needed to load packages into project
```{r load-packages, message = FALSE, eval=TRUE}
library(tidyverse)
library(openintro)
```

## Dr. Arbuthnot's Baptism Records

To get started, run the following command to load the data.

```{r load-abrbuthnot-data, eval=TRUE}
data(arbuthnot)
```

## Exercises

1. What command would you use to extract just the counts of girls baptized? 
    
```{r}

```

2. Is there an apparent trend in the number of girls baptized over the years? 
How would you describe it? (To ensure that your lab report is comprehensive,
be sure to include the code needed to make the plot as well as your written
interpretation.)

```{r plot-girls-vs-year}

```

3. Now, generate a plot of the proportion of boys born over time. What do you see? 


Step 1 : Create new variables `mutate` function
```{r calc-total-bapt-vars-save}

```

Step 2: Plot the data with the `ggplot` function
```{r}
  
```

Step 3: Calculate **mean** of `boy_ratio`
```{r}

```


## Addtional Practice Exercises with USA birth records

Load the present day data with the following command.

```{r load-present-data}
natality <- readr::read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQT4V0JbnhhXh5Ecch1CEBExXEL-MKl-J8TzfOLdFlWoAQ3oCQ2-xCPS5WKPNWraRmwEUiRFSzQclpp/pub?gid=0&single=true&output=csv")
```

4.  What years are included in this data set? What are the dimensions of the 
    data frame? What are the variable (column) names?
```{r}

```

5.  How do these counts compare to Arbuthnot's? Are they of a similar magnitude?

6.  Make a plot that displays the proportion of boys born over time. What do you see? 
    Does Arbuthnot's observation about boys being born in greater proportion than girls 
    hold up in the U.S.? Include the plot in your response. *Hint:* You should be
    able to reuse your code from Exercise 3 above, just replace the dataframe name.

```{r}

```

7.  In what year did we see the most total number of births in the U.S.?
    
```{r}

```

8.  Create a plot of total births over time.  Comment on what do you find interesting?  

```{r}

```


These data come from reports by the Centers for Disease Control. You can learn more about them
by bringing up the help file using the command `?present`.


<div id="license">
This is a product of OpenIntro that is released under a 
[Creative Commons Attribution-ShareAlike 3.0 Unported](http://creativecommons.org/licenses/by-sa/3.0). 
This lab was adapted for OpenIntro by Andrew Bray and Mine &Ccedil;etinkaya-Rundel
from a lab written by Mark Hansen of UCLA Statistics.
</div>
